Visualization for Machine Perception

### 2018-02-08 PAPER/01_related_work.tex
Re-store James edits.
Update some related work.

\section{Related Work}
\cite{linegraph_vs_scatterplot} \cite{cleveland_mcgill}

>>>>

\section{Related Work}

\cite{cleveland_mcgill} Clevenland McGill experiments

\cite{Wang_linegraph_vs_scatterplot} Comparing linegraph vs. scatterplot

\cite{mckenzie_2d_3d} \cite{forsberg2009comparing_3d_vector} \cite{laidlaw_2d_vector} 2D vs. 3D Evaluation (vector fields)

\cite{kindlmann2002color} \cite{rheingans1992color} \cite{ware1988color} \cite{Rogowitz2001_colormaps} color maps

2d vs. 3d + color \cite{borkin2011arteries}

black hat vis \cite{heer2017blackhat}

timeseries \cite{herr2009timeseries}

munzner \cite{munzner2015visualization}

open vs. closed shaped \cite{open_vs_closed_shapes}

visualization ranking \cite{harrison2014_webers_law_rank}

Pineo et al.~\cite{Pineo2012_computational_perception} present a method to automatically evaluating and optimizing visualizations using a computational model of human vision, based on a neural network simulation of the early perceptual processing in the retina and primary visual cortex. [JT] Copied from their abstract.
